\documentclass{article}
\usepackage{hyperref}

\begin{document}
    Array - kinda list \\
    Array 2D - kinda matrix \\
    Array 3D+ - kinda tensor \\

    Binary Plus Tree (B+Tree) - Binary Tree modification, where intermediate nodes dont containt data,
        but values against which actual data is compared and then stored in leaf nodes. \\
    
    Hash function - maps arbitrary sized data to fixed size data. \\

    Set Operations:
    $A = \{1,    3, 4, 5,    7      \}$ \\
    $C = \{1, 2,    4,    6, 7, 8, 9\}$
    \begin{itemize}
        \item Union:         $A \cup       B         = {1, 2, 3, 4, 5, 6, 7, 8, 9}$
        \item Intersect:     $A \cap       B         = {1, 4, 7}$
        \item Except(Minus): $A \backslash B = A - B = {3, 5}$
    \end{itemize}

    Join combines columns from one or more tables. \\
    Relations - inner, outer. \\
    Joins:
    \begin{itemize}
        \item Nested loop \url{https://en.wikipedia.org/wiki/Nested_loop_join}
        \item Merge join \url{https://en.wikipedia.org/wiki/Sort-merge_join}
        \item Hash join \url{https://en.wikipedia.org/wiki/Hash_join}
    \end{itemize}

    Transaction is a single unit of logic or work, sometimes made up of multiple operations.
    Any logical calculation done in a consistent mode in a database is known as a transaction.
    \begin{itemize}
        \item Atomicity   - transaction must either complete in its entirety or have no effect whatsoever
        \item Consistency - transaction must conform to existing constraints in the database
        \item Isolation   - transaction must not affect other transactions
        \item Durability  - transaction must get written to persistent storage
    \end{itemize}

    Isolation levels define the degree to which a transaction must be 
    isolated from the data modifications made by any other transaction in 
    the database system \\

    Levels of transaction isolation:
    \begin{itemize}
        \item Read uncommitted - allows dirty reads(transactions that hasn't been commited yet).
        \item Read committed   - guarantees that any data read is commited at the moment of reading, but allows non repeatable read
            (if row read many times it may contain different data).
        \item Repeatable Read  - transaction holds lock on all rows it is using, allows phantom read
            (same query can return different result in different points in time).
        \item Serializable     - transaction fully locks whole database it works on.
    \end{itemize}
\end{document}